---
title: "R Notebook"
output: html_notebook
---
we are trying here to fit all the transiogram of the co-simulation !

```{r}
library(mvtnorm)
```
```{r}
source("cosim_functions.R")
```


```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```
```{r}
c(pe1,pe2,pe3,pe4)
```


conditional proportions
```{r}

pd1e1=mean(d1*e1,na.rm=TRUE)/pe1
pd1e2=mean(d1*e2,na.rm=TRUE)/pe2
pd1e3=mean(d1*e3,na.rm=TRUE)/pe3
pd1e4=mean(d1*e4,na.rm=TRUE)/pe4

pd2e1=mean(d2*e1,na.rm=TRUE)/pe1
pd2e2=mean(d2*e2,na.rm=TRUE)/pe2
pd2e3=mean(d2*e3,na.rm=TRUE)/pe3
pd2e4=mean(d2*e4,na.rm=TRUE)/pe4

pd3e1=mean(d3*e1,na.rm=TRUE)/pe1
pd3e2=mean(d3*e2,na.rm=TRUE)/pe2
pd3e3=mean(d3*e3,na.rm=TRUE)/pe3
pd3e4=mean(d3*e4,na.rm=TRUE)/pe4

matrix(c(pd1e1,pd1e2,pd1e3,pd1e4,pd2e1,pd2e2,pd2e3,pd2e4,pd3e1,pd3e2,pd3e3,pd3e4),3,4,byrow=TRUE)

```


```{r}
# rv1=0.3
# rv2=1.2
# rhx1=40
# rhx2=40
# b1=0
# b2=5
# rho=0.6
# shift=0.1
# rho1a<-model(shift,rv1,b1)
# warning(rho>rho1a)
# alpha1=(rho/rho1a)^2
# alpha2=1-(rho/rho1a)^2
# rv3=0.2
# rv4=0.3
# rhx3=40
# rhx4=40
# b3=0
# b4=0
# rho34=-0.6
# c=0.
# e=0.65
# a13=-0.
# a14=-0.1
# rho1a14 = model(a14,rv1,b1)

rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*rho1a14*rho
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}

c(qd1e4,qd2e2,qd2e3)

#transiograms
z = (1:300)/100.
t11_model=t12_model=t13_model=t14_model=t21_model=t22_model=t23_model=t24_model=t31_model=t32_model=t33_model=t34_model=t41_model=t42_model=t43_model=t44_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model(d,rv1,b1)+alpha2*model(d,rv2,b2)
    t11_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t12_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t13_model[i]=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    t14_model[i]=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf),upper=c(q1,q2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    t21_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t22_model[i]=pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t23_model[i]=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t24_model[i]=pmvnorm(lower=c(-Inf,q2,q1,-Inf),upper=c(q1,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    t31_model[i]=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t32_model[i]=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t33_model[i]=pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t34_model[i]=pmvnorm(lower=c(q1,q3,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    t41_model[i]=pmvnorm(lower=c(q1,-Inf,-Inf,-Inf),upper=c(Inf,q3,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    t42_model[i]=pmvnorm(lower=c(q1,-Inf,-Inf,q2),upper=c(Inf,q3,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    t43_model[i]=pmvnorm(lower=c(q1,-Inf,q1,q3),upper=c(Inf,q3,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    t44_model[i]=pmvnorm(lower=c(q1,-Inf,q1,-Inf),upper=c(Inf,q3,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
}
par(mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)

t33d_model=t32d_model=t23d_model=t22d_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho34
    Sigma[1,3]=Sigma[3,1]=model(d,rv3,b3)
    Sigma[1,4]=Sigma[4,1]=Sigma[2,3]=Sigma[3,2]=rho34*model(d,rv3,b3)
    Sigma[2,4]=Sigma[4,2]=(rho34^2)*model(d,rv3,b3)+(1-rho34^2)*model(d,rv4,b4)

    t22d_model[i]=pmvnorm(lower=c(qd1,qd2,qd1,qd2),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t23d_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t32d_model[i]=pmvnorm(lower=c(-Inf,-Inf,qd1,qd2),upper=c(qd1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
    t33d_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(qd1,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
}
par(mfrow=c(2,2))
t22d<-tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,t22d_model)
t23d<-tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,t23d_model)
t32d<-tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,t32d_model)
t33d<-tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,t33d_model)

td1e1_model=td1e2_model=td1e3_model=td1e4_model=td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
te1d1_model=te2d1_model=te3d1_model=te4d1_model=te1d2_model=te2d2_model=te3d2_model=te4d2_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model(-d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model(a13+d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model(a14+d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model(a14+d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho
    
    td1e1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e2_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e3_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e4_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    
    td2e1_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    
    te1d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    te2d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    te3d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    te4d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    
    te1d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    te2d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    te3d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    te4d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
}

par(mfrow=c(2,4))
tr_2d_vert(d1,e1,30,nz,0.1)
lines(z,td1e1_model)
tr_2d_vert(d1,e2,30,nz,0.1)
lines(z,td1e2_model)
tr_2d_vert(d1,e3,30,nz,0.1)
lines(z,td1e3_model)
tr_2d_vert(d1,e4,30,nz,0.1)
lines(z,td1e4_model)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

par(mfrow=c(4,2))
tr_2d_vert(e1,d1,30,nz,0.1)
lines(z,te1d1_model)
tr_2d_vert(e2,d1,30,nz,0.1)
lines(z,te2d1_model)
tr_2d_vert(e3,d1,30,nz,0.1)
lines(z,te3d1_model)
tr_2d_vert(e4,d1,30,nz,0.1)
lines(z,te4d1_model)
tr_2d_vert(e1,d2,30,nz,0.1)
lines(z,te1d2_model)
tr_2d_vert(e2,d2,30,nz,0.1)
lines(z,te2d2_model)
tr_2d_vert(e3,d2,30,nz,0.1)
lines(z,te3d2_model)
tr_2d_vert(e4,d2,30,nz,0.1)
lines(z,te4d2_model)

```
beautiful picture for transiograms


```{r}
png(file="latemartransiotest.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
```
we are showing here a figure with the transiograms on the realization
```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemartransiototal.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
lines(z2,t11real,lwd=0.6)
lines(z2,t11real2,lwd=0.6)
lines(z2,t11real3,lwd=0.6)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
lines(z2,t12real,lwd=0.5)
lines(z2,t12real2,lwd=0.5)
lines(z2,t12real3,lwd=0.5)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
lines(z2,t13real,lwd=0.5)
lines(z2,t13real2,lwd=0.5)
lines(z2,t13real3,lwd=0.5)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
lines(z2,t14real,lwd=0.5)
lines(z2,t14real2,lwd=0.5)
lines(z2,t14real3,lwd=0.5)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
lines(z2,t21real,lwd=0.5)
lines(z2,t21real2,lwd=0.5)
lines(z2,t21real3,lwd=0.5)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
lines(z2,t22real,lwd=0.5)
lines(z2,t22real2,lwd=0.5)
lines(z2,t22real3,lwd=0.5)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
lines(z2,t23real,lwd=0.5)
lines(z2,t23real2,lwd=0.5)
lines(z2,t23real3,lwd=0.5)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
lines(z2,t24real,lwd=0.5)
lines(z2,t24real2,lwd=0.5)
lines(z2,t24real3,lwd=0.5)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
lines(z2,t31real,lwd=0.5)
lines(z2,t31real2,lwd=0.5)
lines(z2,t31real3,lwd=0.5)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
lines(z2,t32real,lwd=0.5)
lines(z2,t32real2,lwd=0.5)
lines(z2,t32real3,lwd=0.5)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
lines(z2,t33real,lwd=0.5)
lines(z2,t33real2,lwd=0.5)
lines(z2,t33real3,lwd=0.5)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
lines(z2,t34real,lwd=0.5)
lines(z2,t34real2,lwd=0.5)
lines(z2,t34real3,lwd=0.5)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
lines(z2,t41real,lwd=0.5)
lines(z2,t41real2,lwd=0.5)
lines(z2,t41real3,lwd=0.5)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
lines(z2,t42real,lwd=0.5)
lines(z2,t42real2,lwd=0.5)
lines(z2,t42real3,lwd=0.5)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
lines(z2,t43real,lwd=0.5)
lines(z2,t43real2,lwd=0.5)
lines(z2,t43real3,lwd=0.5)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
lines(z2,t44real,lwd=0.5)
lines(z2,t44real2,lwd=0.5)
lines(z2,t44real3,lwd=0.5)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
```


lets try to fit the embedded transiograms
```{r}
rv1=0.4
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.8
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}
d = 1/5.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model(d,rv1,b1)+alpha2*model(d,rv2,b2)
    r11_model=1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r12_model=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r13_model=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r14_model=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf),upper=c(q1,q2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    r21_model=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r22_model=1-pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r23_model=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r24_model=pmvnorm(lower=c(-Inf,q2,q1,-Inf),upper=c(q1,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r31_model=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r32_model=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r33_model=1-pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r34_model=pmvnorm(lower=c(q1,q3,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r41_model=pmvnorm(lower=c(q1,-Inf,-Inf,-Inf),upper=c(Inf,q3,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r42_model=pmvnorm(lower=c(q1,-Inf,-Inf,q2),upper=c(Inf,q3,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r43_model=pmvnorm(lower=c(q1,-Inf,q1,q3),upper=c(Inf,q3,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r44_model=1-pmvnorm(lower=c(q1,-Inf,q1,-Inf),upper=c(Inf,q3,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    matrix(c(0,r12_model/r11_model,r13_model/r11_model,r14_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r24_model/r22_model,r31_model/r33_model,r32_model/r33_model,0,r34_model/r33_model,r41_model/r44_model,r42_model/r44_model,r43_model/r44_model,0),4,4,byrow=TRUE)
```


trying td2e1, td2e2, td2e3 and td2e4

```{r}
rv1=0.3
rv2=0.5
rhx1=40
rhx2=40
b1=0
b2=0
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=0.8

a14=0.1
rho1a14 = model(a14,rv1,b1)
#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)

qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}

c(qd1e4,qd2e2,qd2e3)

td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)

Sigma = diag(1,5)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=e*rho*model(shift-a14,rv1,b1)/rho1a
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=e*rho*model(d+shift-a14,rv1,b1)/rho1a
    
    td2e1_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,-Inf),upper=c(q1,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e1_model[i]=td2e1_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,-Inf),upper=c(Inf,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e1_model[i]==0){td2e1_model[i]=NA}
    
    td2e2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,q2),upper=c(q1,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=td2e2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2),upper=c(Inf,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e2_model[i]==0){td2e2_model[i]=NA}
    
    td2e3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3),upper=c(q1,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=td2e3_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3),upper=c(Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e3_model[i]==0){td2e3_model[i]=NA}
    
    td2e4_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf),upper=c(q1,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=td2e4_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,-Inf),upper=c(Inf,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e4_model[i]==0){td2e4_model[i]=NA}
}
z = (1:300)/100.
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

```

ok we develop now a more complex model to see if we are able to capture better the co-transiograms of 50dol. 
We add for this a correlation between the second gaussian function and the fourth which slightly complexify the correlation matrix, but not that much. 

```{r}
rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)
#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

c(q1,q2,q3)


Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
qd1e4=0
obje2 = Inf
obje3 = Inf
obje4 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  qd1e4test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  newobje4 =abs( pmvnorm(lower=c(qd1e4test,q1,-Inf),upper=c(Inf,Inf,q3),mean=c(0,0,0),sigma=Sigmad)/pe4 - pd3e4 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
  if (newobje4 < obje4){
    qd1e4 = qd1e4test
    obje4 = newobje4
  }
}

c(qd1e4,qd2e2,qd2e3)

td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
td3e1_model=td3e2_model=td3e3_model=td3e4_model=rep(0,300)

Sigma = diag(1,5)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=(e*rho*model(shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=(e*rho*model(d+shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(d-a24,rv2,b2)
    
    td2e1_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,-Inf),upper=c(q1,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e1_model[i]=td2e1_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,-Inf),upper=c(Inf,Inf,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e1_model[i]==0){td2e1_model[i]=NA}
    
    td2e2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,-Inf,q2),upper=c(q1,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=td2e2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2),upper=c(Inf,Inf,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e2_model[i]==0){td2e2_model[i]=NA}
    
    td2e3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3),upper=c(q1,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=td2e3_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3),upper=c(Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e3_model[i]==0){td2e3_model[i]=NA}
    
    td2e4_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf),upper=c(q1,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=td2e4_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,-Inf),upper=c(Inf,Inf,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2e4_model[i]==0){td2e4_model[i]=NA}
    
    td3e1_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,-Inf,-Inf),upper=c(Inf,q3,Inf,q1,q2),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e1_model[i]==0){td3e1_model[i]=NA}
    td3e2_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,-Inf,q2),upper=c(Inf,q3,Inf,q1,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e2_model[i]==0){td3e2_model[i]=NA}
    td3e3_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,q1,q3),upper=c(Inf,q3,Inf,Inf,Inf),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e3_model[i]==0){td3e3_model[i]=NA}
    td3e4_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,q1,-Inf),upper=c(Inf,q3,Inf,Inf,q3),mean=c(0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3e4_model[i]==0){td3e4_model[i]=NA}
}


z = (1:300)/100.
par(mfrow=c(2,4))
tr_2d_vert(d3,e1,30,nz,0.1)
lines(z,td3e1_model)
tr_2d_vert(d3,e2,30,nz,0.1)
lines(z,td3e2_model)
tr_2d_vert(d3,e3,30,nz,0.1)
lines(z,td3e3_model)
tr_2d_vert(d3,e4,30,nz,0.1)
lines(z,td3e4_model)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)
```

nice figure
```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemarcotransiototal.png",width=3000,height = 1200,res=300)
par(mar=c(2,3,1,1),mfrow=c(2,4))
tr_2d_vert(d3,e1,30,nz,0.1)
lines(z,td3e1_model)
lines(z2,td3e1real,lwd=0.5)
lines(z2,td3e1real2,lwd=0.5)
lines(z2,td3e1real3,lwd=0.5)
title(main=expression(paste('t'[d1e1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d3,e2,30,nz,0.1)
lines(z,td3e2_model)
lines(z2,td3e2real,lwd=0.5)
lines(z2,td3e2real2,lwd=0.5)
lines(z2,td3e2real3,lwd=0.5)
title(main=expression(paste('t'[d1e2],"(h)")),cex.main=2)
tr_2d_vert(d3,e3,30,nz,0.1)
lines(z,td3e3_model)
lines(z2,td3e3real,lwd=0.5)
lines(z2,td3e3real2,lwd=0.5)
lines(z2,td3e3real3,lwd=0.5)
title(main=expression(paste('t'[d1e3],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d3,e4,30,nz,0.1)
lines(z,td3e4_model)
lines(z2,td3e4real,lwd=0.5)
lines(z2,td3e4real2,lwd=0.5)
lines(z2,td3e4real3,lwd=0.5)
title(main=expression(paste('t'[d1e4],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
lines(z2,td2e1real,lwd=0.5)
lines(z2,td2e1real2,lwd=0.5)
lines(z2,td2e1real3,lwd=0.5)
title(main=expression(paste('t'[d2e1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
lines(z2,td2e2real,lwd=0.5)
lines(z2,td2e2real2,lwd=0.5)
lines(z2,td2e2real3,lwd=0.5)
title(main=expression(paste('t'[d2e2],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
lines(z2,td2e3real,lwd=0.5)
lines(z2,td2e3real2,lwd=0.5)
lines(z2,td2e3real3,lwd=0.5)
title(main=expression(paste('t'[d2e3],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,e4,30,nz,0.1)
title(main=expression(paste('t'[d2e4],"(h)")),line=-1,cex.main=2)
lines(z,td2e4_model)
lines(z2,td2e4real,lwd=0.5)
lines(z2,td2e4real2,lwd=0.5)
lines(z2,td2e4real3,lwd=0.5)
```

we need now to look at the auto transiograms of the diagenetic facies 
we use the preceding covariance matrix and add one order
```{r}
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
qd1e4=0
obje2 = Inf
obje3 = Inf
obje4 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  qd1e4test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  newobje4 =abs( pmvnorm(lower=c(qd1e4test,q1,-Inf),upper=c(Inf,Inf,q3),mean=c(0,0,0),sigma=Sigmad)/pe4 - pd3e4 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
  if (newobje4 < obje4){
    qd1e4 = qd1e4test
    obje4 = newobje4
  }
}

td2d2_model=td2d3_model=td3d2_model=td3d3_model=rep(0,300)
Sigma = diag(1,6)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=Sigma[6,4]=Sigma[4,6]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=Sigma[5,6]=Sigma[6,5]=(e*rho*model(shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=(e*rho*model(d+shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(d-a24,rv2,b2)
    Sigma[3,6]=Sigma[6,3]=(e^2)*model(d,rv1,b1)+(f^2)*model(d,rv2,b2)+(1-(e^2)-(f^2))*model(d,rv3,b3)
    Sigma[1,6]=Sigma[6,1]=e*model(d+a14,rv1,b1)
    Sigma[2,6]=Sigma[6,2]=(rho/rho1a)*e*model(d+a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(d+a24,rv2,b2)
    
    td3d3_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,q1,-Inf,qd1e4),upper=c(Inf,q3,Inf,Inf,q3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3d3_model[i]==0){td3d3_model[i]=NA}
    
    td2d2_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,q3,qd2e2),upper=c(q1,Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d2_model[i]=td2d2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,q1,q3,qd2e2),upper=c(Inf,Inf,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d2_model[i]=td2d2_model[i]+pmvnorm(lower=c(q1,q3,qd2e3,-Inf,q2,qd2e2),upper=c(Inf,Inf,Inf,q1,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d2_model[i]=td2d2_model[i]+pmvnorm(lower=c(-Inf,q2,qd2e3,-Inf,q2,qd2e2),upper=c(q1,Inf,Inf,q1,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2d2_model[i]==0){td2d2_model[i]=NA}
    
    td2d3_model[i]=pmvnorm(lower=c(-Inf,q2,qd2e2,q1,-Inf,qd1e4),upper=c(q1,Inf,Inf,Inf,q3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    td2d3_model[i]=td2d3_model[i]+pmvnorm(lower=c(q1,q3,qd2e2,q1,-Inf,qd1e4),upper=c(Inf,Inf,Inf,Inf,q3,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd2
    if(td2d3_model[i]==0){td2d3_model[i]=NA}


  td3d2_model[i]=pmvnorm(lower=c(q1,-Inf,qd1e4,-Inf,q2,qd2e2),upper=c(Inf,q3,Inf,q1,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd3
    td3d2_model[i]=td3d2_model[i]+pmvnorm(lower=c(q1,-Inf,qd1e4,q1,q3,qd2e2),upper=c(Inf,q3,Inf,Inf,Inf,Inf),mean=c(0,0,0,0,0,0),sigma=Sigma)/ pd3
    if(td3d2_model[i]==0){td3d2_model[i]=NA}
}

z = (1:300)/100.
par(mfrow=c(2,2))
tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,td3d3_model)
tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,td3d2_model)
tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,td2d3_model)
tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,td2d2_model)
```

```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemardiagtransiototal.png",width=3000,height = 2000,res=300)
par(mar=c(2,3,1,1),mfrow=c(2,2))
tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,td3d3_model)
lines(z2,td3d3real,lwd=0.5)
lines(z2,td3d3real2,lwd=0.5)
lines(z2,td3d3real3,lwd=0.5)
title(main=expression(paste('t'[d1d1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,td3d2_model)
lines(z2,td3d2real,lwd=0.5)
lines(z2,td3d2real2,lwd=0.5)
lines(z2,td3d2real3,lwd=0.5)
title(main=expression(paste('t'[d1d2],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,td2d3_model)
lines(z2,td2d3real,lwd=0.5)
lines(z2,td2d3real2,lwd=0.5)
lines(z2,td2d3real3,lwd=0.5)
title(main=expression(paste('t'[d2d1],"(h)")),line=-1,cex.main=2)
tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,td2d2_model)
lines(z2,td2d2real,lwd=0.5)
lines(z2,td2d2real2,lwd=0.5)
lines(z2,td2d2real3,lwd=0.5)
title(main=expression(paste('t'[d2d2],"(h)")),line=-1,cex.main=2)
# 
# tr_2d_vert(d3,e1,30,nz,0.1)
# lines(z,td3e1_model)
# title(main=expression(paste('t'[d1e1],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d3,e2,30,nz,0.1)
# lines(z,td3e2_model)
# title(main=expression(paste('t'[d1e2],"(h)")),cex.main=2)
# tr_2d_vert(d3,e3,30,nz,0.1)
# lines(z,td3e3_model)
# title(main=expression(paste('t'[d1e3],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d3,e4,30,nz,0.1)
# lines(z,td3e4_model)
# title(main=expression(paste('t'[d1e4],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e1,30,nz,0.1)
# lines(z,td2e1_model)
# title(main=expression(paste('t'[d2e1],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e2,30,nz,0.1)
# lines(z,td2e2_model)
# title(main=expression(paste('t'[d2e2],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e3,30,nz,0.1)
# lines(z,td2e3_model)
# title(main=expression(paste('t'[d2e3],"(h)")),line=-1,cex.main=2)
# tr_2d_vert(d2,e4,30,nz,0.1)
# title(main=expression(paste('t'[d2e4],"(h)")),line=-1,cex.main=2)
# lines(z,td2e4_model)
```

